---
title: "Lab 2"
author: "[Student Name]"
date: "05-26-20"
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, 
                      message = FALSE, warning = FALSE)
```

# Part 1: Data wrangling

## Introduction

The stop-question-and-frisk (sqf) program, in New York City, is a practice of 
temporarily detaining, questioning, and at times searching civilians and 
suspects. In 2011, the program peaked with a total of 685,724 sqf events.

The NYPD contains data records on every sqf event throughout the program's
history. In this exam we will work with the 2011 sqf data. 
All yearly data and more information about the stop-question-and-frisk 
program can be found at 
https://www1.nyc.gov/site/nypd/stats/reports-analysis/stopfrisk.page.

## Packages

```{r packages}
library(tidyverse)
library(jsonlite)
```

## Data

To get started, read in the data. Each row represents a single sqf event in 
2011.

```{r read_sqf}
sqf <- readRDS("data/sqf_2011.rds")
```

Use object `sqf` to complete the following tasks.

Consult the data dictionary in folder `data_dictionary` of your repo. 
The xlsx file has two tabs with variable descriptions and encoding for every 
variable.

## Tasks

Use functions in package `tidyverse` (`dplyr` and `tidyr`) unless there is 
no Base-R equivalent. Your code should output only the necessary rows and 
variables from the data frame to answer the question or complete the task. 
If the answer is a single number, the result in vector format is fine.

#### Task 1

How many individuals were frisked or searched in the month of August
by precinct 40?

#### Task 2

Create a new variable called `season` according to the following rule

  + spring - March through May
  + summer - June through August
  + fall   - September through November
  + winter - December through February
      
for when an sqf event occurred. Using this new variable, for each season,
what proportion of individuals were frisked for inappropriate attire?

#### Task 3
   
Compute the probability of being involved in an sqf incident for each
race. Compute the conditional probability of being arrested given each
race. For each result, sort the probabilities in descending order.
   
#### Task 4   
   
What was the most common "reason for stop"?

#### Task 5

Compute the median age for those involved in an sqf event for each day of the
week (Sunday - Saturday). *Hint:* Look at functions `mday()`, `month()`,
`day()`, and `wday()` in package `lubridate`. Make a reasonable decision on
how to deal with the obvious incorrect age values.
   
# Part 2: Functionals

## Data

Open Brewery DB is a free API for public information on breweries, cideries, 
brewpubs, and bottleshops. We'll look at a subset of breweries in NC. Later
in this course we'll discuss APIs and how to work with them. For now, read in
the below data. Object `nc_brew` will be a list.

```{r get_nc_brew}
url <- "https://api.openbrewerydb.org/breweries?by_state=north%20carolina&page=1"
nc_brew <- read_json(url)
```

## Tasks

#### Task 1

Print the structure for only the first brewery in the list.

#### Task 2

Use a `for` loop to get the name of each brewery and the URL. Put your result
in a data frame.

#### Task 3

Repeat Task 2, but use an `apply()` function rather than a `for` loop.

#### Task 4

Repeat Task 2, but use a `map*()` function rather than a `for` loop.

#### Task 5

There are many more breweries in NC than what we have in `nc_brew`. We can see
more of them by changing the page number in the URL. For example,
https://api.openbrewerydb.org/breweries?by_state=north%20carolina&page=2 will
show all the breweries on "page 2". The below function will allow you to
get the breweries on any specified page.

```{r get_breweries}
get_breweries <- function(page = 1) {
  base_url <- "https://api.openbrewerydb.org/breweries?by_state=north%20carolina&page="
  url <- str_c(base_url, page)
  
  read_json(url)
}
```

Use a `map*()` function to get all the breweries on the first 10 pages. Save the
result as an object named `nc_breweries_200`.

#### Task 6

Use a `map*()` function to get the name for each brewery in `nc_breweries_200`.
Have your final result be a character vector of length 200.
